---
title: "Data Analysis"
author: "Rahul"
date: "September 26, 2016"
output: html_document
fig.width: 900
---

# 900K observations extracted randomly.Below is the summary and Glimpse of the Data.
```{r summary, echo=FALSE, warning=FALSE, message=FALSE, fig.width=900}
library(ggplot2)
library(gridExtra)
library(tidyr)
library(dplyr)
df_train_random <- read.csv('C:\\Users\\rahuaror\\Documents\\Rahul\\SpingBoard\\HugeDataSet\\train_random.csv')

# Summary of Data
summary(df_train_random)
glimpse (df_train_random)

```


## Feature of Interest **"Adjusted Demand".**
#### Looking at its distribution using a log scale on the x axis since data seems skewed.
######Warning - Removed 16187 rows containing non-finite values (stat_bin).
######There are 16187 occurences of Zero(0) which were removed.
```{r plots-histogram, echo=FALSE, warning=FALSE, message=FALSE}

ggplot(data = df_train_random, aes( x = Adjusted_Demand ) ) +  
  geom_histogram( bins = 30 ) +scale_x_log10()

```

## Using **_Box-Plot_** to see the **Outliers**
######Warning : Removed 16187 rows containing non-finite values (stat_boxplot).
```{r box, echo=FALSE, warning=FALSE, message=FALSE }
ggplot(data = df_train_random, aes( x = 1, y = Adjusted_Demand ) ) +  
  geom_boxplot()   +scale_y_log10()

```

### As per observation **Adjusted Demand** > 10 has outliers, hence taking a subset of the data.

```{r subset, warning=FALSE, message=FALSE}

# Taking a subset of Demand less than 10
df_train_random_subset <- subset(df_train_random, Adjusted_Demand < 10 )

```

### **Adjusted Demand** subset data's **_Box-Plot_** and **_Summary_**
```{r sub-box, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}
ggplot(data = df_train_random_subset, aes( x = 1, y = Adjusted_Demand ) ) +  
  geom_boxplot()   +scale_y_log10()

summary(df_train_random_subset$Adjusted_Demand)

```

## Observe Relationship between **Adjusted Demand** and **other Features** 

###Relation between **Product ID** and **Adjusted Demand**
###### Used subset data of Adjusted Demand
```{r plots-product, warning=FALSE, message=FALSE, cache=TRUE}
#See outliers in Product ID
ggplot(data = df_train_random_subset, aes( x = 1, y = Product_ID ) ) +  
  geom_boxplot() +scale_y_log10()


# Scatter Plot distribution between Adjusted Demand and Product ID colored by Week.
ggplot(data = df_train_random_subset, aes( x = Product_ID, y = Adjusted_Demand ) ) +  
             geom_jitter(aes(colour = factor(Week_number)))

```

###Relation between **Client ID** and **Adjusted Demand**
###### Used subset data of Adjusted Demand

```{r plots-client, warning=FALSE, message=FALSE, cache=TRUE}
# See Outliers in Client ID
ggplot(data = df_train_random_subset, aes( x = 1, y = Client_ID ) ) +  
  geom_boxplot() +scale_y_log10()

# Scatter Plot distribution between Adjusted Demand and Client ID colored by Week.
ggplot(data = df_train_random_subset, aes( x = Client_ID, y = Adjusted_Demand ) ) +  
             geom_jitter(aes(colour = factor(Week_number)))
```

### Relation between **Sales unit this week** and **Adjusted Demand**
######Warning: Removed 3620 rows containing non-finite values (stat_boxplot).
```{r plots-SalesUnit, warning=FALSE, message=FALSE, cache=TRUE}
# See Outliers in Sales Unit
ggplot(data = df_train_random_subset, aes( x = 1, y = Sales_unit_this_week ) ) +  
  geom_boxplot() +scale_y_log10()

# Scatter Plot distribution between Adjusted Demand and Sales Unit colored by Week.
ggplot(data = df_train_random_subset, aes( x = Sales_unit_this_week, y = Adjusted_Demand ) ) +  
             geom_jitter(aes(colour = factor(Week_number)))

```

### Relation between **Returns unit next week** and **Adjusted Demand**
###### Warning: Removed 714155 rows containing non-finite values (stat_boxplot)
```{r plots-ReturnsUnit, warning=FALSE, message=FALSE, cache=TRUE}
# See Outliers in Returns Unit
ggplot(data = df_train_random_subset, aes( x = 1, y = Returns_unit_next_week ) ) +  
  geom_boxplot() +scale_y_log10()

# Scatter Plot distribution between Adjusted Demand and Returns Unit colored by Week.
ggplot(data = df_train_random_subset, aes( x = Returns_unit_next_week, y = Adjusted_Demand ) ) +  
             geom_jitter(aes(colour = factor(Week_number)))

```

### Relation between **Route ID** and **Adjusted Demand**
```{r plots-RouteID, warning=FALSE, message=FALSE, cache=TRUE}
# See Outliers in Route ID
ggplot(data = df_train_random_subset, aes( x = 1, y = Route_ID ) ) +  
  geom_boxplot() +scale_y_log10()

# Scatter Plot distribution between Adjusted Demand and Route ID colored by Week.
ggplot(data = df_train_random_subset, aes( x = Route_ID, y = Adjusted_Demand ) ) +  
             geom_jitter(aes(colour = factor(Week_number)))

```

### Relation between **Sales Channel ID** and **Adjusted Demand**
```{r plots-SalesChannel, warning=FALSE, message=FALSE, cache=TRUE}
# See Outliers in Sales Channel ID
ggplot(data = df_train_random_subset, aes( x = 1, y = Sales_Channel_ID ) ) +  
  geom_boxplot() +scale_y_log10()

# Scatter Plot distribution between Adjusted Demand and Sales Channel ID colored by Week.
ggplot(data = df_train_random_subset, aes( x = Sales_Channel_ID, y = Adjusted_Demand ) ) +  
             geom_jitter(aes(colour = factor(Week_number)))

# Scatter Plot distribution between Adjusted Demand and Week number colored by Sales Channel ID
ggplot(data = df_train_random_subset, aes( x = Week_number, y = Adjusted_Demand ) ) +  
             geom_jitter(aes(colour = factor(Sales_Channel_ID)))

```

### Relation between **Sales Depot ID** and **Adjusted Demand**
```{r plots-Salesdepot, warning=FALSE, message=FALSE, cache=TRUE}
# See Outliers in Sales Depot ID
ggplot(data = df_train_random_subset, aes( x = 1, y = Sales_Depot_ID ) ) +  
  geom_boxplot() +scale_y_log10()

# Scatter Plot distribution between Adjusted Demand and Sales Depot ID colored by Week.
ggplot(data = df_train_random_subset, aes( x = Sales_Depot_ID, y = Adjusted_Demand ) ) +  
             geom_jitter(aes(colour = factor(Week_number)))


```

### Relation between **Week number** and **Adjusted Demand**
```{r plots-week, warning=FALSE, message=FALSE, cache=TRUE}
# See Outliers in Week number
ggplot(data = df_train_random_subset, aes( x = 1, y = Week_number ) ) +  
  geom_boxplot() +scale_y_log10()

# Scatter Plot distribution between Adjusted Demand and Week number.
ggplot(data = df_train_random_subset, aes( x = Week_number, y = Adjusted_Demand ) ) +  
             geom_jitter()

```