---
title: "Products"
author: "Rahul"
date: "October 5, 2016"
output: html_document
---

# Summary of Data.
```{r summary, echo=FALSE, warning=FALSE, message=FALSE}
library(ggplot2)
library(gridExtra)
library(tidyr)
library(dplyr)
df_train_random <- read.csv('C:\\Users\\rahuaror\\Documents\\Rahul\\SpingBoard\\HugeDataSet\\train_random.csv')

## Summary of Data
summary(df_train_random)

```

## Frequency (Occurence) of Product ids sorted descending
```{r Product, echo=FALSE, warning=FALSE}

Prod_freq <- as.data.frame(table(df_train_random$Product_ID))

## Products Frequency
ggplot(Prod_freq, aes(x= reorder(factor(Var1), -Freq), y = Freq))+
      geom_bar(stat="identity")+
      scale_x_discrete("Product_ID") + scale_y_log10() +
      theme(axis.text.x=element_blank(),
            axis.ticks.x=element_blank())
```

## Product Summary, 
###Each Product's Mean/Median/1st Quartile/3rd Quartile for Adjusted Demand, sorted descending by Frequncy
```{r Prod_summary, echo=FALSE, warning=FALSE}
                 
Products_summary <- df_train_random %>% group_by(Product_ID) %>%
                    summarise(  Freq = n(),
                    Sales_Unit = sum(Sales_unit_this_week),
                    Mean_AD = mean(Adjusted_Demand),
                    Median_AD = median(Adjusted_Demand),
                    Quartile_1 = quantile(Adjusted_Demand, 0.25),
                    Quartile_3 = quantile(Adjusted_Demand, 0.75)) %>%
                    arrange(desc(Mean_AD))

glimpse(Products_summary)


grid.arrange(ggplot(Products_summary, aes (x= reorder(factor(as.character(Product_ID)), -Freq)))+
      geom_point(aes(y = Mean_AD), col = "blue", alpha = 0.5)+
      scale_x_discrete(names("Product_ID")) +
      theme(axis.text.x=element_blank(),
            axis.ticks.x=element_blank()), 
      ggplot(Products_summary, aes (x= reorder(factor(as.character(Product_ID)), -Freq)))+
      geom_point(aes(y = Median_AD), col = "red", alpha = 0.5)+
      scale_x_discrete(names("Product_ID")) +
      theme(axis.text.x=element_blank(),
            axis.ticks.x=element_blank()), 
      ggplot(Products_summary, aes (x= reorder(factor(as.character(Product_ID)), -Freq)))+
      geom_point(aes(y = Quartile_1), col = "coral4", alpha = 0.5)+
      scale_x_discrete(names("Product_ID")) +
      theme(axis.text.x=element_blank(),
            axis.ticks.x=element_blank()),
       ggplot(Products_summary, aes (x= reorder(factor(as.character(Product_ID)), -Freq)))+
      geom_point(aes(y = Quartile_3), col = "purple", alpha = 0.5)+
      scale_x_discrete(names("Product_ID")) +
      theme(axis.text.x=element_blank(),
            axis.ticks.x=element_blank()), ncol = 2, nrow = 2)
      
```

### As per above charts, there are some Product ids with very Low frequency(occurence) and very high Mean/Median.

```{r freq, echo=FALSE, warning=FALSE}

head(arrange(Products_summary, desc(-Freq)))
```

### There are some Product ids with very high frequency(occurence) and low Mean/Median values.

```{r freq_2, echo=FALSE, warning=FALSE}

tail(arrange(Products_summary, desc(-Freq)))
```
